Trends of downward SDR in Thessaloniki 

### 2023-04-25 Article.Rmd
Commit 2023-04-25 10:17

......

<!-- Data selection -->
Due to larger measurement uncertainty near the horizon, we exclude
all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we remove data with Azimuth angle between 
$35^\circ$ and $120^\circ$ and SZA greater than $80^\circ$. At 
those cases the Sun, were not visible by the instruments.

@@

To make the measurements comparable throughout the dataset. 
<!-- 1au -->
We adjusted all 1-minute values to the mean Sun and Earth distance.
<!-- TSI -->
<!-- And, we made all measurements relative to the TSI at 1au, in order to compensate for the the Suns intensity variability, using an homogenized timeseries of satellite TSI observations. As a result, we processed all radiation data as a fraction of Suns TSI. -->

<!-- Clear Sky -->
In this analysis, we need .............
, we using two selection of our measurements dataset, one with all sky conditions (ALL),
consisting of the whole available data, and one filtered for 'clear sky' 
conditions (CS). The latter was created, using a method adapted to our 
site, and was proposed by @Long2000 and by @Reno2016.

>>>>

In order to estimate the effect of the clouds on the global radiation we create three datasets. 
The all sky conditions containing all the valid measurements. 
The clear-sky conditions data and the remainder part the cloudy condition data. 
To identify the clear-sky conditions we used a method proposed by @Long2000 and by @Reno2016 that was adapted and configured for the site.

@@

### Data selection

Due to a significant measurement uncertainty near the horizon, we exclude
all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we exclude data with Azimuth angle between 
$35^\circ$ and $120^\circ$ and SZA greater than $80^\circ$.
At those cases the Sun systematically, is not visible by the instruments.

To make the measurements comparable throughout the dataset. 
<!-- 1au -->
We adjusted all 1-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
<!-- And, we made all measurements relative to the TSI at 1au, in order to compensate for the the Suns intensity variability, using an homogenized timeseries of satellite TSI observations. As a result, we processed all radiation data as a fraction of Suns TSI. -->

### Process and aggregation of radiometric data
